---
title: "S4Examples: A Package for S4 Examples"
author:
- name: Bioconductor Maintainer
  affiliation: The Bioconductor Project
  email: maintainer@bioconductor.org
package: S4Examples
output:
  BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{S4Examples: An Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# S4Examples

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    collapse = TRUE, comment = "#>"
)
```

## Introduction

The `S4Examples` package provides a simple example of an S4 class. It inherits
from the `SimpleList` class in the `r BiocStyle::Biocpkg("S4Vectors")` package.

## Installation

To install the `S4Examples` package, use the following command:

```{r install, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("Bioconductor/S4Examples")
```

**Note**. Currently, the package is only hosted on GitHub.

## S4Examples Load

```{r example-load,warning=FALSE,message=FALSE}
library(S4Examples)
library(S4Vectors)
```

## S4Example Usage

Using a `list` as the input to the constructor function `Example`: 

```{r example-usage}
Example(list(a = 1, b = 2, c = 3))
```

Using a `SimpleList` as the input to the constructor function `Example`:

```{r example-simple}
Example(SimpleList(a = 1, b = 2, c = 3))
```

## Methods

The `longForm` method is used to create a long form of the `Example` class.

```{r example-methods}
ex <- Example(list(a = 1, b = 2, c = 3))
longForm(ex)
```

## Validity

The `Example` class has a validity function that checks the following:

- All element names must be in the alphabet.

```{r, example-alpha,error=TRUE}
Example(list(hello = 1))
```

- All elements in the `Example` object must have the same length.

```{r example-error2,error=TRUE}
Example(list(a = 1, b = 2, c = 3:4))
```

- All element names must be lower case.

```{r example-error,error=TRUE}
Example(list(A = 1, b = 2, c = 3))
```

Here is a correct example of the `Example` class:

```{r example-validity}
Example(list(x = 24, y = 25, z = 26))
```

# Session info

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
